\documentclass[man,floatsintext,donotrepeattitle]{apa6}
\frenchspacing
\raggedbottom
\title{README for Clayton Stanley's dissertation}
%\shorttitle{Comparing memory models of tag retrieval}
\shorttitle{README}
\author{Clayton Stanley}
\affiliation{Rice University}
\usepackage[group-separator={,}]{siunitx}

\usepackage{csquotes}
\usepackage[style=apa,sortcites=true,sorting=nyt,backend=biber,doi=false,uniquename=false]{biblatex}
\DeclareLanguageMapping{american}{american-apa}
\usepackage[american]{babel}
\addbibresource{bibliography.bib}

%\usepackage{enumitem}
\usepackage{paralist}
\usepackage[doublespacing]{setspace}
\usepackage{tocloft}

\begin{document}
\maketitle

\section{Description}

\input{../src/public.tex}

\section{Configuring environment}

\subsubsection{Git Repositories}

There are two main git repositories for this work.
The main repository contains all of the source code but very little source data.
This repo is located on chil under ``srv/git/stanley-dissertation.git''.
The source data was separated from the source code for two reasons:
First, the size of the source data is much larger than the code, so if someone wants to look at just the source, it takes much less time to clone the source repo with this method.
Second, the source data for Twitter should not be made public, due to Twitter's terms of service,
and to encourage replication and transparency of research, the source code is publicized and available on GitHub.
So the source data cannot be included in this public repository.

The source repo is included as a submodule of the main repository, but in order to access it, you have to have credentials on the chil server.
This way access to the repository can be limited, but the repo is still properly linked to the main repository.

\subsubsection{Setting Up Environment}

First, clone the main repository:

\begin{singlespace}
\begin{compactitem}
  \item \emph{git clone ssh://[chil uname]@chil.rice.edu/srv/git/stanley-dissertation}:
    Clone the main repository.
\end{compactitem}
\end{singlespace}

Then, cd to the top level of the repository and run the following commands to configure the environment:

\begin{singlespace}
\begin{compactitem} 
  \item \emph{./check-dev-env.sh}:
    Ensures that ssh keys, hostname alias, binary dependencies, etc. are all configured properly.
    If this isn't run first, none of the following commands will work.
  \item \emph{git submodule update --init --recursive}:
    Initialize and update all submodules.
    This will pull in the source data submodule.
  \item \emph{make -C submodules/dissertationData pull}:
    Get additional compressed source data for the source data repo.
    This includes large .csv text data extracted from the postgres tables.
    These .csv files are too large to be tracked with git.
  \item \emph{make -C submodules/dissertationData extract}:
    Uncompress the compressed source data.
\end{compactitem}
\end{singlespace}

If you want this done all in one go, run the \emph{make post-clone} command at the top level of the repository:
You'll need a version of make installed to do this.
\emph{check-dev-env} checks for this binary dependency and includes a suggestion on how to install make if you don't have it.

\subsubection{Manual Environment Setup}

Setting up the postgres tables is currently not automated.
This involves creating the tables, all indexes, importing the .csv tables from the source data repository, and then updating the tables with a few additional columns.
This process \emph{was} documented in the form of a script, but that script hasn't been tested.
It contains code for both creating the tables and updating columns in the tables.
Those steps must be done separately, and the tables should be imported into postgres before the updates are called.
Currently that script is located in ``dissProject/createTables.sql''.
I figure that no one other than myself will want to get the database configured,
since the results of all the model runs are saved in separate .csv files and the db is not required to analyze or visualize them.
If I ever have to confiure the database on another machine for this research, I'll separate the ``createTables.sql'' file into two separate files, 
automate and test the whole process, and create an additional make target to configure the db.

\printbibliography[heading=bibintoc]

\end{document}
